An OSGi-based Sensor Network for \\ Environmental Monitoring

### 2009-03-02 docs/icccn2009/paper.tex
NetBEAMS architecture
git-svn-id: svn://localhost/netbeams/trunk@318 559edde2-a4d4-44e0-96fc-4035e40d7396
Intro, Conclusion, and updated NetBEAMS diagram
git-svn-id: svn://localhost/netbeams/trunk@327 559edde2-a4d4-44e0-96fc-4035e40d7396

The introduction should emphasize that we interpret sensor networks in
a different way: our focus is on off-the-shelf, highly specialized
sensors for environmental monitoring. Our focus is end-to-end: how to
collect data from a remote location with no stationary power or
Internet connection and deliver the data in near-realtime to a web
browser. Length: first page (including title and abstract).

@@

@@

>>>>

Environmental monitoring depends on the reliable collection of
measurements from remotely deployed sensors and the rapid transfer of
those measurements to data centers where processing and analysis may
take place. Typically, sensors are deployed in out-of-the-way
locations where physical access is limited and connections for
telemetry are poor or nonexistent.   Maintaining the data stream from
these sensors places demands on human resources, requiring site visits
to service the sensors and to download data stored on internal memory.
Consequently, there is a lag of days to months between the time the
sensors perform the measurements and the time the measurements becomes
available.   Advances in battery life and anti-fouling technology have
extended service cycles for field sensors, with the unwanted result of
further delaying access to monitoring data.  In addition, the
dependence on field site visits to alter of sensor characteristics,
such as sampling rate, prevents adjustment in monitoring strategy in
response to rapidly developing events (e.g. oil spills, harmful algal
blooms).

To address these problems of data collection from remote
sensors, we propose to develop an automated end-to-end system based on
proven technology that provides a means to program and interrogate
sensors at the remote field locations and to transmit collected
measurements over long distances to data collections centers where the
data is rapidly processed, archived, and made available to potential
users in near real-time.

@@

\begin{figure*}
\centering
\epsfig{file=netbeams, width=10cm}
\caption{\label{FIG_NETBEAMS} NetBEAMS architecture.}
\end{figure*}

@@

The California coastal region is populated by a vast number of
remotely deployed sensors that monitor environmental conditions
ranging from weather to water quality to ocean surface currents.
These sensors are operated by data providers, including resource
management groups, research scientists, municipalities, and state and
federal agencies, who could use near real-time data streams to inform
decision that impact public health, public safety, and the protection
of resources.  In addition, there are efforts underway at the state
and federal level to collate the data collected by the individual data
providers into integrated monitoring networks that will enhance the
distribution of monitoring data to public, private, and federal users
groups.  Success of these efforts, whether small scale or a large
integrated network, depends on the first step in the data management
process: reliably obtaining data in near real-time from remotely
located sensors.  This step can be the weak link in the data
management pathway when telemetry options are unreliable.  The
availability of a plug-and-play computing platform designed to
communicate with a variety of sensor types and to provide data
telemetry to distant brick and mortar data centers would stabilize
data streams with poor telemetry and allowing expansion of sensor
coverage into regions not presently served.  The low power consumption
and low cost of these units would be particularly beneficial for
applications with long service cycles and for data providers trying to
maintain data streams on a limited budget.
